An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-14 VLDB2026/main.tex
Update main.tex

	\textit{\textbf{Different Datasets.}}  
	To evaluate the performance of various methods across different datasets, we conduct experiments on 6 datasets. Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.

	As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset. Because Audio has small scale, low dimensionality, and low LID. In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset. Because these two datasets have the largest scale and highest LID.

>>>>

	\textit{\textbf{Different Datasets.}}  
	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset for out-of-distribution (OOD) queries. Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.

	As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset. Because Audio has small scale, low dimensionality, and low LID. In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset besides the OOD dataset Text2Image. Because these two datasets have the largest scale and highest LID.
